---

title : Sales Forecast Regression Exercise
author : INSEAD MBA Core Course UDJ
job : INSEAD
widgets : []
mode : standalone 

---

## The Problem

A marketing manager wishes to forecast corporate sales for the coming year and to understand better the factors that influence them. 

---
## Sales Drivers

The manager believes that sales depend upon

personal disposable income, dealers' allowances prices, product development expenditures, capital investments, advertising, sales expenses, total industry advertising, and some random effects.

---

## The Data

1.  Personal Disposable Income in Millions of Dollars. (PDI)

2.	Dealers' Allowances in Thousands of Dollars. (DEALS)

3.	Price in Dollars. (PRICE)

4.	Product Development in Thousands of Dollars. (R&D)

5.	Capital Investments in Thousands of Dollars. (INVEST)

6.	Advertising in Thousands of Dollars. (ADVERTIS)

7.	Sales Expenses in Thousands of Dollars. (EXPENSE)

8.	Total Industry Advertising in Thousands of Dollars. (TOTINDAD)

9.	Company Sales in Thousands of Dollars. (SALES)

---

## Summary Statistics

<div class="row">
<div class="col-md-6">
```{r echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis'}
data_summary = my_summary(ProjectData[,union(dependent_variable,independent_variables),drop=F])
print(xtable(data_summary, caption = "Summary Statistics", digits=3), type = "html", html.table.attributes = "class='table table-striped table-hover table-bordered'", caption.placement = "top", comment = FALSE, include.rownames = TRUE)
```
</div>
</div>

---

## Histogram of the Dependent Variable `r dependent_variable`

```{r echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis'}
hist(ProjectData[,dependent_variable], main = paste("Histogram of", dependent_variable, sep=" "), xlab=dependent_variable,breaks = max(5,round(nrow(ProjectData)/5)))
```

---

## Time Series of Sales

An **interactive chart** of the `r dependent_variable` time series (Place the mouse on the plot to see daily values, and zoom using click-and-drag with the mouse in the smaller graph below)


```{r echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis'}
Sales = ProjectData[,dependent_variable]
thedates=1:nrow(ProjectData)
data.frame.series<-data.frame(Time=thedates, Values=Sales, row_names=rownames(ProjectData))
int_series <- nvd3Plot(Values ~ Time, data = data.frame.series, id = 'chart', type = 'lineWithFocusChart')
int_series$yAxis(showMaxMin=FALSE)
int_series$print(include_assets = TRUE, cdn = TRUE)
```

---

## Correlation Matrix

```{r echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis'}
data_reorder=cbind(ProjectData[,independent_variables,drop=F],ProjectData[,dependent_variable,drop=F])
thecor=cor(data_reorder)
colnames(thecor)<-colnames(thecor)
rownames(thecor)<-rownames(thecor)

cat(renderHeatmapX(thecor, border=1))
```

---
## Just one of the many possible plots...


```{r echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis'}
yax=colnames(ProjectData[,independent_variables,drop=F])[1]
plot(ProjectData[,yax],ProjectData[,dependent_variable], xlab=yax, ylab=dependent_variable)
```

---

## Our Regression Model


```{r echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis'}

if (length(independent_variables) == 1){ 
  regression_model_to_see = paste(dependent_variable, paste("b1",independent_variables,sep="*"), sep=" = ")
  } else {
    res=paste(make_b(1),independent_variables[1], sep="*")
    for (iter in 2:(length(independent_variables)-1))
      res=paste(res,paste(make_b(iter),independent_variables[iter],sep="*"), sep=" + ")
    res=paste(res,paste(make_b(length(independent_variables)),tail(independent_variables,1),sep="*"), sep=" + ")
    regression_model_to_see = paste(dependent_variable, res, sep=" = ")  
    }
cat(regression_model_to_see)
```



---

## Regression Output
```{r echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis'}
if (length(independent_variables) == 1){ 
  regression_model=paste(paste(dependent_variable, "~",sep=""), independent_variables,sep="")
  } else {
    res=independent_variables[1]
    for (iter in 2:(length(independent_variables)-1))
      res=paste(res,independent_variables[iter],sep="+")
    res=paste(res,tail(independent_variables,1),sep="+")
    regression_model = paste(dependent_variable, res, sep="~")  
    }

the_fit<-lm(regression_model,data=ProjectData)
print_the_fit<-as.list(summary(the_fit))
fit_table<-xtable(summary(the_fit),caption=paste("Regression Analysis - Dependent variable",dependent_variable, sep=""))
print(fit_table,type="html",html.table.attributes = "class='table table-striped table-hover table-bordered'",caption.placement="top")
```

R-squared: `r print_the_fit$r.squared` ,  Adjusted R-squared: `r print_the_fit$adj.r.squared` 

F-statistic: `r print_the_fit$fstatistic["value"]` with   `r print_the_fit$fstatistic["numdf"]` and `r print_the_fit$fstatistic["dendf"]` degrees of freedom 

Residual standard error: `r sqrt(deviance(the_fit)/df.residual(the_fit))` with `r the_fit$df` degrees of freedom

---

## The Residuals Plot (Time Series)


```{r echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis'}

the_residuals = residuals(the_fit) 

thedates=1:nrow(ProjectData)
data.frame.series<-data.frame(Time=thedates, Residual=the_residuals, row_names=rownames(ProjectData))
residual_series <- nvd3Plot(Residual ~ Time, data = data.frame.series, id = 'chart', type = 'lineWithFocusChart')
residual_series$yAxis(showMaxMin=FALSE)
residual_series$print(include_assets = TRUE, cdn = TRUE)
```

---

## One of the many Residual plots...


```{r echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis'}
plot(ProjectData[,dependent_variable],the_residuals,xlab=dependent_variable,ylab="Residuals")
abline(0, 0, col="red")  
```

---

## Histogram of the Residuals


```{r echo=FALSE, comment=NA, warning=FALSE, message=FALSE,results='asis'}
hist(the_residuals, main = "Histogram of the Residuals", xlab=dependent_variable,breaks = max(5,round(length(the_residuals)/5)))
```

